
matching caesarean script
-------------------------

N.Green

17/04/13



```{r}
## suppress warning message
options(warn=-1)

setwd("H:\\caesarean SSI LOS")

survData <- read.table(".\\raw data\\data.txt")

## read-in matching look-up table
## and convert to list type
matches <- as.data.frame( t(read.table(".\\processed data\\Match LOS Mar 13.txt",fill=TRUE)))
colnames(matches) <- matches[1,]
matches <- matches[-1,]
matches <- as.list(matches)
matches <- lapply(matches, function(x) x[!is.na(x)] )
matches
```


```{r}
## helper function
## difference between each infected case and mean of matched samples
meandiff <- function(matches, survData){
# LOSar: time from admission to departure
  
  diff <- c(NULL, NULL)
  for (serialno in names(matches)){
    diff <- rbind(diff, c(serialno, survData$LOSar[survData$serialnumber==serialno]-
                            mean(survData$LOSar[survData$serialnumber%in%matches[[serialno]]]))
    )
  }

diff
}

## standard error
## by jackknifing matching table (leave-one-out)
matches.se <- function(matches, survData){
  out <- NULL
  for (i in 1:length(matches)){
    for (j in 1:length(matches[[i]])){
      matches.temp <- matches
      matches.temp[[i]] <- matches.temp[[i]][-j]
      out <- c(out, mean(as.numeric(meandiff(matches.temp, survData)[,2]), na.rm=TRUE))
    }
  }
  sqrt(var(out))
}

```


# individual difference

```{r}
meandiff(matches, survData)
```

# overall expected excess LOS

```{r}
mean(as.numeric(meandiff(matches, survData)[,2]))
suppressWarnings(matches.se(matches, survData))
```



# include matching by overall length of stay prior to infection

LOSar>=LOSpreop+days2inf
update matching look-up table

```{r}
matches.ar <- matches

for (serialno in names(matches)){
	matches.ar[[serialno]] <- matches.ar[[serialno]][survData$LOSar[survData$serialnumber%in%matches.ar[[serialno]]] >=
					 	(survData$LOSpreop[survData$serialnumber==serialno]+
						 survData$days2inf[survData$serialnumber==serialno]) ]
}
matches.ar
```


# individual difference

```{r}
meandiff(matches.ar, survData)
```

# overall expected excess LOS inclding LOSar

```{r}
mean(as.numeric(meandiff(matches.ar, survData)[,2]), na.rm=TRUE)
suppressWarnings(matches.se(matches.ar, survData))
```



# include matching by postop length of stay prior to infection

LOSop>=days2inf
update matching look-up table

```{r}
matches.ar <- matches
for (serialno in names(matches)){
  matches.ar[[serialno]] <- matches.ar[[serialno]][survData$LOSop[survData$serialnumber%in%matches.ar[[serialno]]] >=
                                                   survData$days2inf[survData$serialnumber==serialno] ]
}
matches.ar
```

# individual difference

```{r}
meandiff(matches.ar, survData)
```

# overall expected excess LOS inclding LOSar

```{r}
mean(as.numeric(meandiff(matches.ar, survData)[,2]), na.rm=TRUE)
suppressWarnings(matches.se(matches.ar, survData))
```
